Proof part 1: 3 layers

### 2023-10-03 No Diamond for 3 layers.tex
Update No Diamond for 3 layers.tex
Delete some error lines
test
lili
proof

First we consider the case when there are only three layers: input layer, one hidden layer, and output layer. For convenience, we assume that the output only has one node. Of course, we assume all active functions are ReLU function.

@@

Put all together, when all $c_j$ of sign $+,-$ gets values $s(c_j)$, $b_i=\sum_{c_j}W_{b_ic_j}s(c_j)+B_i$ gets its actual upper bounds and DeepPoly upper bounds, and then  $\bar{f_i}(b_i)=\ReLU(b_i)$, the actual value of $\hat{b}_i$. This is what we want to show.

\subsubsection*{negative}Now we consider a node $b_i$ that $W_{xb_i}<0$. All are similar. Now, each $W_{b_ic_j}$ has the opposite sign of $c_j$. So when all $c_j$ of $+,-$ sign get $s(c_j)$ value, $b_i$ also gets its lower bound and DeepPoly lower bound. By the assumption, when $b_i$ gets its DeepPoly lower bound, $\underline{f_i}(b_i)=\ReLU(b_i)$.

151+124+103+48+3(estimate)=428

0 : 1, 6.942969230753979, 933.6970219612122

open 30 : 59 : -1, 1.3304800987255705, 213.07373809814453, DiamondMin of Min: -2.4831832946871297

open 0:   59 : -1, 2.2208665044849285, 110.11069464683533, DiamondMin of Min: -3.2142924202998118

open 20:  59 : -1, 1.5128416712774397, 169.37895846366882, DiamondMin of Min: -2.5436423082465973

open 40: 59 : -1, 1.1588057492305743, 167.29228901863098, DiamondMin of Min: -2.322909620171307

open 50: 59 : -1, 1.1332793237397172, 216.03394603729248, DiamondMin of Min: -2.3194345600969135

open 50: 59 : -1, 1.136410977665245, 250.3934416770935, DiamondMin of Min: -2.3194345600969135

open 50 (more data): 59 : -1, 1.1033637386628505, 321.2751393318176, DiamondMin of Min: -2.279701100000497

open 10: 59 : -1, 1.7965610184250298, 144.45073246955872, DiamondMin of Min: -2.8121700263290466

%random open 10: 59 : -1, 2.0868988971016167, 133.93379545211792, DiamondMin of Min: -3.070953068366777

%random open 20: 59 : -1, 1.9800122543451073, 130.6924500465393, DiamondMin of Min: -3.0701026929909143
%
%random open 20: 59 : -1, 1.97995359889014, 135.06353521347046, DiamondMin of Min: -2.9642806539605853

random open 21: 59 : -1, 1.8202823109335369, 158.56950044631958, DiamondMin of Min: -2.926562550850029

random open 21: 59 : -1, 1.8113843758166142, 128.9297330379486, DiamondMin of Min: -2.986175395636058

random open 31: 59 : -1, 1.617607152194705, 142.7976849079132, DiamondMin of Min: -2.7544434938921665

random open 31: 59 : -1, 1.6338272022581422, 147.04282569885254, DiamondMin of Min: -2.734869999570412

random open 41: 59 : -1, 1.4376834177337172, 141.38413166999817, DiamondMin of Min: -2.591134103101991

random open 51: 59 : -1, 1.2285876079490041, 218.22643494606018, DiamondMin of Min: -2.461825229746404

random open 61: 59 : -1, 1.0442270697364395, 315.7167875766754, DiamondMin of Min: -2.219210859797969

random open 61: 59 : -1, 1.0458496294859592, 375.4530429840088, DiamondMin of Min: -2.219210859797969

>>>>

\begin{definition}
	A pair of paths $(\pi,\pi')$
	is called {\em compensating} if they start in the same neuron $a$ and ends in the same neuron $z$, and the product of weights over $\pi$ is strictly positive and the product of weights over $\pi'$ is strictly negative.
\end{definition}

Intuitively, compensating paths will partially cancel out each other as they conribute the same weight $w(a)$ to the weight of the same neuron $w(z)$, but with opposite sign. 
It is not simple to take this compensation into account because of ReLUs: the particular compensation will depend upon the weight of intermediate nodes seen along $\pi$ and $\pi'$, 
as when one of this node gets negative input, it will clip it to 0.

\begin{theorem}
	If for all $(a,d)$ there is no compensation paths $(\pi,\pi')$ 
	in the network from $a$ to $d$, then the LP approximation is 
	$100\%$ accurate (or deepoly with the $f(x) \geq 0$ abstraction only, never using the 
	$f(x) \geq x$ abstraction). 
\end{theorem}

\begin{proof}
First we consider the case when there are only three layers: input layer, one hidden layer, and output layer. For convenience, we assume that the output only has one node. Of course, we assume all active functions are ReLU function.

@@

Put all together, when all $c_j$ of sign $+,-$ gets values $s(c_j)$, $b_i=\sum_{c_j}W_{b_ic_j}s(c_j)+B_i$ gets its actual upper bounds and DeepPoly upper bounds, and then  $\bar{f_i}(b_i)=\ReLU(b_i)$, the actual value of $\hat{b}_i$. This is what we want to show.
\end{proof}

\subsubsection*{negative}Now we consider a node $b_i$ that $W_{xb_i}<0$. All are similar. Now, each $W_{b_ic_j}$ has the opposite sign of $c_j$. So when all $c_j$ of $+,-$ sign get $s(c_j)$ value, $b_i$ also gets its lower bound and DeepPoly lower bound. By the assumption, when $b_i$ gets its DeepPoly lower bound, $\underline{f_i}(b_i)=\ReLU(b_i)$. This is what we want to show.
